The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2016-02-20 script/de/chapters/cryptomethods.tex
Some typos

Dieses Kapitel soll einen eher beschreibenden Einstieg bieten und die
Grundlagen ohne Verwendung von allzuviel Mathematik vermitteln.

@@

\vskip +3pt
Manchmal werden auch zwei weitere Konzepte verwendet:

@@

Beispiel: Aktuell wissen wir, dass RSA\index{RSA} höchstens so schwierig
ist wie die Faktorisierung, aber wir können nicht beweisen, dass es genauso
schwierig ist.
Deshalb hat RSA keine beweisbare Mindest-Sicherheit. Oder in anderen Worten:
Wir können nicht beweisen, dass wenn das Kryptosystem RSA gebrochen ist, dass
dann auch die Faktoriserung (ein schwieriges mathematisches Problem) gelöst
werden kann.

>>>>

Dieses Kapitel soll einen eher beschreibenden Einstieg bieten und die
Grundlagen ohne Verwendung von allzu viel Mathematik vermitteln.

@@

\vskip +3pt
\noindent Manchmal werden auch zwei weitere Konzepte verwendet:

@@

Beispiel: Aktuell wissen wir, dass RSA\index{RSA} höchstens so schwierig
ist wie die Faktorisierung, aber wir können nicht beweisen, dass es genauso
schwierig ist.
Deshalb hat RSA keine beweisbare Mindest-Sicherheit. Oder in anderen Worten:
Wir können nicht beweisen, dass wenn das Kryptosystem RSA gebrochen ist, dass
dann auch die Faktorisierung (ein schwieriges mathematisches Problem) gelöst
werden kann.

### 2016-02-20 script/en/chapters/cryptomethods.tex
Some typos

\vskip +3pt
Two more concepts are sometimes used:

@@

In 2009 Biryukov und Khovratovich \cite{cm:Biryukov2009} published another
theoretical attack on AES. This attack uses different methods from the ones
described above. They applied methods from hash function cryptanalysis (local
collisions and boomerang switching) to construct a related-key attack on
AES-256. I.~e.\ the attacker not only needs to be able to encrypt arbitrary data
(chosen plain text), in addition he needs to be able to manipulate the unknown key
(related-key).

@@

Brute-force (exhaustive search, trial-and-error) means to completely examine all keys of the key space: so no special analysis methods have to be used. Instead, the ciphertext is decrypted with all possible keys%
\footnote{%
    With CT1\index{CrypTool 1} you can also perform brute-force attacks
    of modern symmetric algorithms (using the menu path
    {\bf Analysis \textbackslash{} Symmetric Encryption (modern)}): Here
    the weakest knowledge of an attacker is assumed, he performs a 
    ciphertext-only attack.\\
    With CT2\index{CrypTool 2} you can also perform brute-force attacks
    (using the templates under {\bf Cryptanalysis \textbackslash{} Modern}).
    Highly powerful is the KeySearcher component, which can be used to
    distribute the calculations to many different computers.
}
and for each resulting text it is checked, whether this is a meaningful clear text%
\footnote{%
    If the cleartext is written in a natural language and at least 100 B
    lobg, this check also can be performed automatically.\\
    To achieve a result in an appropriate time with a single PC you should 
    mark not more than 24 bit of the key as unknown.
}.
A key length of 64 bit means at most $2^{64}$ = 18,446,744,073,709,551,616 or about 18 trillion (GB) / 18 quintillion (US)  keys to check\index{CrypTool}.

>>>>

\vskip +3pt
\noindent Two more concepts are sometimes used:

@@

In 2009 Biryukov and Khovratovich \cite{cm:Biryukov2009} published another
theoretical attack on AES. This attack uses different methods from the ones
described above. They applied methods from hash function cryptanalysis (local
collisions and boomerang switching) to construct a related-key attack on
AES-256. I.~e.\ the attacker not only needs to be able to encrypt arbitrary data
(chosen plain text), in addition he needs to be able to manipulate the unknown key
(related-key).

@@

Brute-force (exhaustive search, trial-and-error) means to completely examine all keys of the key space: so no special analysis methods have to be used. Instead, the ciphertext is decrypted with all possible keys%
\footnote{%
    With CT1\index{CrypTool 1} you can also perform brute-force attacks
    of modern symmetric algorithms (using the menu path
    {\bf Analysis \textbackslash{} Symmetric Encryption (modern)}): Here
    the weakest knowledge of an attacker is assumed, he performs a 
    ciphertext-only attack.\\
    With CT2\index{CrypTool 2} you can also perform brute-force attacks
    (using the templates under {\bf Cryptanalysis \textbackslash{} Modern}).
    Highly powerful is the KeySearcher component, which can be used to
    distribute the calculations to many different computers.
}
and for each resulting text it is checked, whether this is a meaningful clear text%
\footnote{%
    If the cleartext is written in a natural language and at least 100 B
    long, this check also can be performed automatically.\\
    To achieve a result in an appropriate time with a single PC you should 
    mark not more than 24 bit of the key as unknown.
}.
A key length of 64 bit means at most $2^{64}$ = 18,446,744,073,709,551,616 or about 18 trillion (GB) / 18 quintillion (US)  keys to check\index{CrypTool}.

### 2016-02-20 script/en/chapters/paper_and_pencil.tex
Some typos

         This P\&P cipher creates a key stream which is so good, that even
         nowadays it is hard to crack the cipher if you don't know the
         originally sortierted card deck (ciphertext-only attack).\\

>>>>

         This P\&P cipher creates a key stream which is so good, that even
         nowadays it is hard to crack the cipher if you don't know the
         originally sorted card deck (ciphertext-only attack).\\
